---
title: "Examples using googleVis"
author: "Celine Hernandez"
date: "22 Jan 2015"
output: html_document
---

### Example of making a table in RMarkdown

Experiment | Type
---------- | ----------
0 | Wild type
1 | KO
2 | Wild type
3 | KO

Simple, not very impressive, though. This can be improved using the xtable package, to get a nicer rendering. But the table will still be static. Another solution is to use the googleVis library.


```{r, warning=FALSE, echo=FALSE}
suppressPackageStartupMessages(library(googleVis))
```

```{r , echo=FALSE, results='asis'}
irisTable <- gvisTable(iris[, c(5, 1:4)], 
    options = list(width = 400, height = 300))

print(irisTable, "chart")
```

### Another test : dispalying line charts

First a simple example.

```{r, results='asis'}
df=data.frame(country=c("US", "GB", "BR"), 
              val1=c(10,13,14), 
              val2=c(23,12,32))

Line <- gvisLineChart(df)
print(Line, "chart")
```

Then a slightly more complex one, with two different scales. 

```{r, echo=FALSE, results='asis'}
Line2 <- gvisLineChart(df, "country", c("val1","val2"),
                       options=list(
                         series="[{targetAxisIndex: 0},
                                 {targetAxisIndex:1}]",
                         vAxes="[{title:'val1'}, {title:'val2'}]"
                       ))
print(Line2, "chart")
```


### Other possible elements


```{r, echo=FALSE, results='asis'}

Bubble <- gvisBubbleChart(Fruits, idvar="Fruit", 
                          xvar="Sales", yvar="Expenses",
                          colorvar="Year", sizevar="Profit",
                          options=list(
                            hAxis='{minValue:75, maxValue:125}'))
print(Bubble, "chart")

Candle <- gvisCandlestickChart(OpenClose, 
                               options=list(legend='none'))
print(Candle, "chart")

Pie <- gvisPieChart(CityPopularity)
print(Pie, "chart")

Intensity <- gvisIntensityMap(df)
print(Intensity, "chart")

Tree <- gvisTreeMap(Regions,  
                    "Region", "Parent", 
                    "Val", "Fac", 
                    options=list(fontSize=16))
print(Tree, "chart")

Geo=gvisGeoChart(Exports, locationvar="Country", 
                 colorvar="Profit",
                 options=list(projection="kavrayskiy-vii"))
print(Geo, "chart")
GeoMarker <- gvisGeoChart(Andrew, "LatLong", 
                          sizevar='Speed_kt',
                          colorvar="Pressure_mb", 
                          options=list(region="US"))
print(GeoMarker, "chart")

AndrewMap <- gvisMap(Andrew, "LatLong" , "Tip", 
                     options=list(showTip=TRUE, 
                                  showLine=TRUE, 
                                  enableScrollWheel=TRUE,
                                  mapType='terrain', 
                                  useMapTypeControl=TRUE))
print(AndrewMap, "chart")

datSK <- data.frame(From=c(rep("A",3), rep("B", 3)),
                    To=c(rep(c("X", "Y", "Z"),2)),
                    Weight=c(5,7,6,2,9,4))

## Sankey chart
Sankey <- gvisSankey(datSK, from="From", to="To", weight="Weight",
                     options=list(
                       sankey="{link: {color: { fill: '#d799ae' } },
                            node: { color: { fill: '#a61d4c' },
                            label: { color: '#871b47' } }}"))
print(Sankey, "chart")


## Timeline
datTL <- data.frame(Position=c(rep("President", 3), rep("Vice", 3)),
                    Name=c("Washington", "Adams", "Jefferson",
                           "Adams", "Jefferson", "Burr"),
                    start=as.Date(x=rep(c("1789-03-29", "1797-02-03", 
                                          "1801-02-03"),2)),
                    end=as.Date(x=rep(c("1797-02-03", "1801-02-03", 
                                        "1809-02-03"),2)))

Timeline <- gvisTimeline(data=datTL, 
                         rowlabel="Name",
                         barlabel="Position",
                         start="start", 
                         end="end",
                         options=list(timeline="{groupByRowLabel:false}",
                                      backgroundColor='#ffd', 
                                      height=350,
                                      colors="['#cbb69d', '#603913', '#c69c6e']"))
print(Timeline, "chart")

## Calendar

Cal <- gvisCalendar(Cairo, 
                    datevar="Date", 
                    numvar="Temp",
                    options=list(
                      title="Daily temperature in Cairo",
                      height=320,
                      calendar="{yearLabel: { fontName: 'Times-Roman',
                               fontSize: 32, color: '#1A8763', bold: true},
                               cellSize: 10,
                               cellColor: { stroke: 'red', strokeOpacity: 0.2 },
                               focusedCellColor: {stroke:'red'}}")
)
print(Cal, "chart")
```

